| Base de datos de abejas Ibéricas \n| Iberian Bees database\n

### 2022-02-11 manuscript/manuscript.Rmd
Update general files
Small tweaks

author: Ignasi Bartomeus^1^, Thomas Woods^2^, Luisa Carvalheiro^3^, and a lot of coauthors^4^

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../data/metadata/attributes.csv")
kable(metadata)
```

>>>>

author: Ignasi Bartomeus^1^, Jose B. Lanuza, Thomas Woods^2^, Luisa Carvalheiro^3^, and a lot of coauthors^4^

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../data/metadata/attributes.csv")
kable(metadata[,-1])
```
